Improving the Reliability of the Pavlovian \break Go/No-Go Task

### 2023-07-20 manuscript/main.tex
fix minor typo in abstract

\noindent \textbf{Background:} The Pavlovian go/no-go task is commonly used to measure individual differences in Pavlovian biases and their interaction with instrumental learning. However, prior research has found suboptimal reliability in computational model-based performance measures for this task, limiting its usefulness in individual-differences research. These studies did not make use of several strategies that previously shown to enhance task-measure reliability (e.g., task gamification, hierarchical Bayesian modeling for model estimation). Here we investigated if such approaches could improve the task's reliability.\\

\noindent \textbf{Methods:} Across two experiments, we recruited two independent samples of adult participants (N=103, N=110) to complete two novel, gamified versions of the Pavlovian go/no-go task multiple times over several weeks. We used hierarchical Bayesian modeling to derive reinforcement learning model-based indices of participants' task performance, and additionally to estimate the reliability of these measures.\\

>>>>

\noindent \textbf{Background:} The Pavlovian go/no-go task is commonly used to measure individual differences in Pavlovian biases and their interaction with instrumental learning. However, prior research has reported suboptimal reliability for computational model-based performance measures for this task, limiting its usefulness in individual-differences research. These studies did not make use of several strategies previously shown to enhance task-measure reliability (e.g., task gamification, hierarchical Bayesian modeling for model estimation). Here we investigated if such approaches could improve the task's reliability.\\

\noindent \textbf{Methods:} Across two experiments, we recruited two independent samples of adult participants (N=103, N=110) to complete a novel, gamified version of the Pavlovian go/no-go task multiple times over several weeks. We used hierarchical Bayesian modeling to derive reinforcement learning model-based indices of participants' task performance, and additionally to estimate the reliability of these measures.\\
